% EBMA paper for Political Analysis: Full (unblinded) version 
% Written by: Jacob M. Montgomery, Florian Hollenbach, and Michael
% D. Ward.
% Last update on: 15/12/2011
% Last updated : Florian & Mike


%\documentclass[pdftex,12pt,fullpage,oneside,endnotes]{amsart}
\documentclass[12pt,fullpage,endnotes]{article}

\usepackage{array,amsmath,psfrag,amssymb,subfigure,tabularx}
\usepackage{hyperref,multicol}
\usepackage{pa}
\usepackage{booktabs}
%\usepackage{vmargin,boxedminipage}
\usepackage[usenames]{color}
\usepackage{datetime}
\usepackage{dcolumn}
\usepackage{wrapfig}
\usepackage{setspace}
\usepackage{url}
\usepackage[english]{babel}
\usepackage{times}
\usepackage{multirow}
\usepackage[pdftex]{graphicx}
\usepackage{lscape}
%\usepackage[top=1in,right=1in,left=1in,bottom=1in]{geometry}
\usepackage{array}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{endnotes}

%\graphicspath{ Project"/"NSF BMA"/graphics/}} % change to nsf
\newcommand{\note}[1]{\endnote{\doublespacing#1 \vspace{4 mm}}}

\usepackage{natbib}
\bibpunct{(}{)}{;}{a}{}{,}
\bibdata{Flo_Bib}

\newboolean{blind}
\setboolean{blind}{false}


\title{Improving Predictions Using Ensemble \\ Bayesian Model
  Averaging\thanks{For generously sharing their data and models with
    us, we thank Alan Abramowitz, James Campbell, Robert Erikson, Ray
    Fair, Douglas Hibbs, Michael Lewis-Beck, Andrew D. Martin, Kevin
    Quinn, Stephen Shellman, Charles Tien, \& Christopher Wlezien.
    This project was undertaken in the framework of an initiative
    funded by the Information Processing Technology Office of the
    Defense Advanced Research Projects Agency aimed at producing
    models to provide an Integrated Crisis Early Warning Systems
    (ICEWS) for decision makers in the U.S. defense community. The
    holding grant is to the Lockheed Martin Corporation, Contract
    FA8650-07-C-7749. All the bad ideas and mistakes are our own. 
    We especially want to thank Adrian Raftery and Brendan Nyhan for their
    encouragement and feedback as this project evolved. The editor and the reviewers of {\em Political Analysis}
    provided especially salient and important suggestions that substantially improved our research. }}
\author{
Jacob M. Montgomery\\
	Department of Political Science\\
	Washington University in St. Louis\\
	Campus Box 1063, One Brookings Drive\\
	St. Louis, MO, USA, 63130-4899 
	\and
Florian Hollenbach  \\
	Department of Political Science\\
	Duke University\\
	Perkins Hall 326 Box 90204\\
	Durham, NC, USA, 27707-4330
	\and
Michael D. Ward\\
	Department of Political Science\\
	Duke University\\
	Perkins Hall 326 Box 90204\\
	Durham, NC, USA, 27707-4330\\
	corresponding author: michael.d.ward@duke.edu
} 




\date{\today}


\begin{document}

\maketitle
\thispagestyle{empty}
\clearpage
\pagestyle{myheadings}
\markright{Montgomery, Hollenbach, \& Ward\hfill Ensemble BMA\hfill}
\newpage
\singlespacing

\thispagestyle{empty}


\begin{abstract}
\begin{doublespace}
\input{EBMASubmissionABSTRACT.tex}
\end{doublespace}
\end{abstract}

\doublespacing
\newpage

%%% Insert all of the main text
\setcounter{page}{1}
\include{EBMASubmissionBody}




%%Bib 
\singlespacing
\bibliographystyle{chicago}
%\bibliography{Flo_Bib,masterEBMA}
\bibliography{Flo_Bib}

\theendnotes

\newpage

\listoffigures

\input{EBMASubmissionTables}
\clearpage
\input{EBMASubmissionFigures}


%\bibdata{"Volumes/"ICEWS Project"/"NSF BMA"/flo_Bib","/Volumes/"ICEWS Project"/"NSF BMA"/masterEBMA"}
%\bibliography{/Users/mw160/Documents/BIBTEXFILES/predictionrefs/predictions2,/Users/mw160/Documents/BIBTEXFILES/2009mdwbib}}



%Contact information for authors:

\end{document}
\bye
